Glue-on AdS holography for $T\bar T$-deformed CFTs

### 2023-08-26 alpha/GlueonAdS/glueon-poster-v2.tex
Add qr-code & finalize poster

\textbf{Caveat:} the duality only admits $\zeta_c > 0$ so $\mu < 0$.\\
But \TTbar itself admits $\mu > 0$ with cool properties.

@@

\vspace*{-4\baselineskip}
\begin{center}
	\mbox{
		\hspace{-3em}
		\includegraphics[width=1.19\linewidth]{img/ads-cft-cutoff.png}
	}

@@

\parbox{\linewidth}{
\vspace{-\baselineskip}
\textbf{\begin{equation*}
\hspace{-3em}
\begin{aligned}
	\textrm{Cutoff}
	\ &/\ %
	\text{\textit{glue-on} $\mrm{AdS}_3$ Gravity}
	\!\!&\equiv\ %
	\textrm{\TTbar deformed $\mrm{CFT}_2$ at $\mcal{N}_{\zeta_c}$} \\
	\zeta_c > 0
	\ &/\ %
	\zeta_c < 0
	& \mu \in \mbb{R}\hspace{1em}\,
\end{aligned}
\end{equation*}}
\begin{center}
	\vspace{-1\baselineskip}%
	\centering
	\includegraphics[width=.65\linewidth]{img/diagram.pdf}

	\vspace{-.5\baselineskip}
	\scriptsize\ Top-down view of a constant $t$ slice
\end{center}
%\vspace{-\baselineskip}
}

@@

	\item \textbf{\textit{State-dependent} maps of \mbox{coordinates}}
	\begin{align}
		dt' &= \sqrt{ \big(1 - \zeta_c (T_u+T_v)^2 \big) \big(1 - \zeta_c (T_u-T_v)^2 \big) } \, dt, \notag \\
		 d\varphi' &= d\varphi + \zeta_c \big( T_u^2 - T_v^2 \big)\,dt.
	\label{eq:state_dependent_map}
	\end{align}
	$\leadsto$ correct charges, the modified signal propagation speed $v'_{\pm} \equiv \pm {d\varphi'}/{dt'}$, and \TTbar \textbf{thermodynamics} when Wick rotated. In particular,
	\begin{equation*}
	\hspace{-.5em} \mu > 0,\ \ \,
		T_L(\mu)\,T_R(\mu) \le - \frac{1}{4\pi^2 \ell^2 \zeta_c} = \frac{3}{4\pi^2c\mu} = T_H(\mu)^2.
	\end{equation*}
	$T_{L,R}$: temperatures associated with $u',v' = \varphi' \pm t'$.\\
	$T_H$: the \textit{Hagedorn temperature}: exceeding $T_H$ leads to a complex entropy.

@@

\item \textbf{Torus:} {modular invariance} \& sparseness of the ``light'' spectrum at large $c$ leads to the universal form :
	\begin{equation*}\small
	\hspace{-2em}
		\log   Z_{T\bar T}(\mu)  \approx \left\{ \begin{aligned}
		& {-\frac{1}{2}}\,(\beta_L + \beta_R)\, RE_{\text{vac}}(\mu),  &\beta_L \beta_R > 1, \\
		& {-2 \pi^2 \bigg(\frac{1}{\beta_L} + \frac{1}{\beta_R}\bigg)  RE_{\text{vac}}\bigg(\frac{4\pi^2}{\beta_L \beta_R} \mu \bigg)},  &\beta_L\beta_R < 1. %\\[2ex]
		 \end{aligned} \right. %\label{ZTTbar}
	\end{equation*}
	\citations{\noindent%
		\textcite{Datta:2018thy}\\
		\textcite{Apolo:2023aho}\\
		cf.~\textcite{Hartman:2014oaa}
%		\textcite{Apolo:2023aho}, \mbox{following \textcite{Datta:2018thy} and \textsl{\citeauthor{Hartman:2014oaa}}}
	}

\item \textbf{Sphere:} maximally symmetric,\\ \mbox{\footnotesize \textcite{Donnelly:2018bef}}
	\begin{equation}
%		\label{sphere:stresstensor}
		\langle T_{ij}\rangle = -\frac{1}{4\pi\mu} \bigg(1-\sqrt{1-\frac{c\mu}{3R^2}}\, \bigg)  \gamma_{ij}.
	\end{equation}
Trace relation: \mbox{$
%	\begin{align*}
%\partial_\mu \log Z_{\TTbar}(\mu)&=8\pi \int d^2x\sqrt{\gamma}\, \langle T\bar{T} \rangle \\
(-R)\,\partial_R \log Z_{\TTbar}(\mu)=\int d^2x\sqrt{\gamma}\,\langle T^i_i \rangle
%	\end{align*}
$} and the flow equation \eqref{TTbardef} 
admit the general \mbox{solution} with a $\mu$-\textit{independent} integration constant $a$:
	\begin{equation*}\small
	\hspace{-1.3em}
		\log Z_{\TTbar}(\mu, a) = \tfrac{c}{3} \log \Big[\tfrac{R}{a}   \Big(1+\sqrt{1-\tfrac{c \mu }{3  R^2}}\, \Big) \Big] - \tfrac{R^2}{\mu}  \sqrt{1-\tfrac{c \mu }{3 R^2}} + \tfrac{R^2}{\mu}. %\label{Zsol}
	\end{equation*}
	\begin{itemize}%[noitemsep]
	\item $a = \sqrt{c|\mu|/3}$: \mbox{recover {\footnotesize \textcite{Donnelly:2018bef}}} \\
	$a = \epsilon$: also a valid choice, where the the RG length scale $\epsilon$ is decoupled from $\mu$.

@@

	\item Future: understand the \textbf{entanglement structure} of \TTbar deformation with the help of bulk geometry.
	\begin{flushright}
		\vspace{-.5\baselineskip}
		\citations{
			\textcite{Lewkowycz:2019xse}
		}
	\end{flushright}
\end{itemize}
\centering\vspace{-.8\baselineskip}
\includegraphics[width=.6\linewidth]{img/RT-AdS.pdf}

\vspace{-1.2\baselineskip}
{\footnotesize RT surface for the extended $\mrm{AdS}_3$}

%
%\citations{
%\begin{itemize}[noitemsep]
%\item \textcite{He:2023xnb}
%\item \textcite{He:2023wko}
%\item \textcite{Tian:2023fgf}
%\end{itemize}
%}
%
%\renewcommand*{\bibfont}{\footnotesize}
%\printbibliography %%% should not specify heading

>>>>

\textbf{Caveat:} the duality only admits $\zeta_c > 0$ so $\mu < 0$.\\
But \TTbar itself admits $\mu > 0$ with nice properties.

@@

\vspace*{-4\baselineskip}
\begin{center}
	\mbox{
		\hspace{-2.6em}
		\includegraphics[width=1.17\linewidth]{img/ads-cft-cutoff.png}
	}

@@

\parbox{\linewidth}{
\vspace{-\baselineskip}
\textbf{\begin{equation*}
\hspace{-3em}
\begin{aligned}
	\textrm{Cutoff}
	\ &/\ %
	\text{\textit{glue-on} $\mrm{AdS}_3$ Gravity}
	\!\!&\equiv\ %
	\textrm{\TTbar deformed $\mrm{CFT}_2$ at $\mcal{N}_{\zeta_c}$} \\
	\zeta_c > 0
	\ &/\ %
	\zeta_c < 0
	& \mu \in \mbb{R}\hspace{1em}\,
\end{aligned}
\end{equation*}}
\begin{center}
	\vspace{-1\baselineskip}%
	\centering
	\includegraphics[width=.7\linewidth]{img/diagram.pdf}

	\vspace{-.45\baselineskip}
	\scriptsize\ Top-down view of a constant $t$ slice
\end{center}
%\vspace{-\baselineskip}
}

@@

	\item \textbf{\textit{State-dependent} maps of \mbox{coordinates}}
	\begin{align}
		dt' &= \sqrt{ \big(1 - \zeta_c (T_u+T_v)^2 \big) \big(1 - \zeta_c (T_u-T_v)^2 \big) } \, dt, \notag \\
		 d\varphi' &= d\varphi + \zeta_c \big( T_u^2 - T_v^2 \big)\,dt.
	\label{eq:state_dependent_map}
	\end{align}
	$\leadsto$ correct charges, the modified signal propagation speed $v'_{\pm} \equiv \pm {d\varphi'}/{dt'}$, and \TTbar \textbf{thermodynamics} upon Wick rotation. In particular,
	\begin{equation*}
	\hspace{-.5em} \mu > 0,\ \ \,
		T_L(\mu)\,T_R(\mu) \le - \frac{1}{4\pi^2 \ell^2 \zeta_c} = \frac{3}{4\pi^2c\mu} = T_H(\mu)^2.
	\end{equation*}
	$T_{L,R}$: temperatures associated with $u',v' = \varphi' \pm t'$.\\
	$T_H$: the \textit{Hagedorn temperature}: exceeding $T_H$ leads to a complex entropy.

@@

\item \textbf{Torus:} {modular invariance} \& sparseness of the ``light'' spectrum at large $c$ $\leadsto$ universal form:
	\begin{equation*}\small
	\hspace{-2em}
		\log   Z_{T\bar T}(\mu)  \approx \left\{ \begin{aligned}
		& {-\frac{1}{2}}\,(\beta_L + \beta_R)\, RE_{\text{vac}}(\mu),  &\beta_L \beta_R > 1, \\
		& {-2 \pi^2 \bigg(\frac{1}{\beta_L} + \frac{1}{\beta_R}\bigg)  RE_{\text{vac}}\bigg(\frac{4\pi^2}{\beta_L \beta_R} \mu \bigg)},  &\beta_L\beta_R < 1. %\\[2ex]
		 \end{aligned} \right. %\label{ZTTbar}
	\end{equation*}
	\begin{flushright}
		\vspace{-.5\baselineskip}
		\citations{\noindent%
			\textcite{Datta:2018thy}\\
			\textcite{Apolo:2023aho}\\
			cf.~\textcite{Hartman:2014oaa}
		}
		\vspace{-.5\baselineskip}
	\end{flushright}

\item \textbf{Sphere:} maximally symmetric,\\[-1.4\baselineskip]

\hfill\mbox{\footnotesize \textcite{Donnelly:2018bef}}
	\begin{equation}
%		\label{sphere:stresstensor}
		\langle T_{ij}\rangle = -\frac{1}{4\pi\mu} \bigg(1-\sqrt{1-\frac{c\mu}{3R^2}}\, \bigg)  \gamma_{ij}.
	\end{equation}
Trace relation: \mbox{$
%	\begin{align*}
%\partial_\mu \log Z_{\TTbar}(\mu)&=8\pi \int d^2x\sqrt{\gamma}\, \langle T\bar{T} \rangle \\
(-R)\,\partial_R \log Z_{\TTbar}(\mu)=\int d^2x\sqrt{\gamma}\,\langle T^i_i \rangle
%	\end{align*}
$} and the flow equation \eqref{TTbardef} 
admit the general \mbox{solution} with a $\mu$-\textit{independent} integration constant $a$:
	\begin{equation*}\small
	\hspace{-1.3em}
		\log Z_{\TTbar}(\mu, a) = \tfrac{c}{3} \log \Big[\tfrac{R}{a}   \Big(1+\sqrt{1-\tfrac{c \mu }{3  R^2}}\, \Big) \Big] - \tfrac{R^2}{\mu}  \sqrt{1-\tfrac{c \mu }{3 R^2}} + \tfrac{R^2}{\mu}. %\label{Zsol}
	\end{equation*}
	\begin{itemize}%[noitemsep]
	\item $a = \sqrt{c|\mu|/3}$: \mbox{recover {\small
		\textsl{\citeauthor{Donnelly:2018bef}}
		\cite{Donnelly:2018bef}
	}} \\
	$a = \epsilon$: also a valid choice, where the the RG length scale $\epsilon$ is decoupled from $\mu$.

@@

	\item Future: understand the \textbf{entanglement structure} of \TTbar deformation with the help of bulk geometry.
	\begin{flushright}
		\vspace{-.5\baselineskip}
		\citations{
			\textcite{Lewkowycz:2019xse}
		}
	\end{flushright}
\end{itemize}
\centering\vspace{-1\baselineskip}
\includegraphics[width=.6\linewidth]{img/RT-AdS.pdf}

\vspace{-1\baselineskip}
{\footnotesize RT surface for the extended $\mrm{AdS}_3$}

\vspace{.8\baselineskip}
\hrule
\vspace{.1\baselineskip}

\hspace{-.7em}
\begin{minipage}[c]{.81\linewidth}
\begin{itemize}[noitemsep,leftmargin=5em]\small
\item[\texttt{Email:}]
	\url{bryanlais@gmail.com}
\item[\texttt{Inspire:}]
	\href{https://inspirehep.net/authors/2640135}{
		\texttt{inspirehep.net/authors/2640135}
	}
\item[\texttt{GitHub:}]
	\href{https://github.com/bryango}{
		\texttt{github.com/bryango}
	}
\end{itemize}
\end{minipage}%
\hfill%
\begin{minipage}{.17\linewidth}
\includegraphics[width=\linewidth]{img/inspire-qr.png}
\end{minipage}%
~\mbox{}
